|

### 2024-10-15 posts/BarthPapageorgeThom/BPT.qmd
Completed BPT.html for RG2024/10/15

1. Into genotyping: Older, more educated, more females, wealthier [(Table S1)](BarthPapgergeThome_SNPWealth_JPE2020Appendix.pdf#page=5) 
   * Education $\SIM$ genotyping &rArr; individuals with low EA scores have higher than average education  &rArr; attenuates EA score $\SIM$ education gradient

@@

2. Of using retired households: More precise wealth but smaller sample size/more selection [(Table 3)](BarthPapgergeThome_SNPWealth_JPE2020.pdf#page=17) 
   * Selection results in more males, older in high EA scores &lArr; (Male) higher EA scorers live longer, but modest in size (Panel A)
   * Age band of retired HHs &uarr; than main sample &rArr; q4-q1 differences (more selection) &uarr; &rArr; EA score $\SIM$ education gradient &uarr; (Panel A vs. B)
   * $+$non-retired HHs &rArr; q4-q1 differences &darr; (less selection) &rArr; EA score $\SIM$ education gradient &darr; (Panel A vs. C)
   * Smaller degree of selection leads to smaller q4-q1 differences
   * But larger measurement errors in wealth ($\because$ pensions, etc. are not measured)

@@

> However, the magnitudes of these differences are similar and relatively modest across alternate samples. Restricting our sample to retired households balances concerns about sample selection and measurement error. 
[(p.19)](BarthPapgergeThome_SNPWealth_JPE2020.pdf#page=19)

>>>>

1. Into genotyping: Older, more educated, more females, wealthier [(Table S1)](BarthPapageorgeThom_SNPWealth_JPE2020Appendix.pdf#page=5) 
   * Education $\SIM$ genotyping &rArr; individuals with low EA scores have higher than average education  &rArr; attenuates EA score $\SIM$ education gradient

@@

2. Of using retired households: More precise wealth but smaller sample size/more selection [(Table 3)](BarthPapageorgeThom_SNPWealth_JPE2020.pdf#page=17) 
   * Selection results in more males, older in high EA scores &lArr; (Male) higher EA scorers live longer, but modest in size (Panel A)
   * Age band of retired HHs &uarr; than main sample &rArr; q4-q1 differences (more selection) &uarr; &rArr; EA score $\SIM$ education gradient &uarr; (Panel A vs. B)
   * $+$non-retired HHs &rArr; q4-q1 differences &darr; (less selection) &rArr; EA score $\SIM$ education gradient &darr; (Panel A vs. C)
   * Smaller degree of selection leads to smaller q4-q1 differences
   * But larger measurement errors in wealth ($\because$ pensions, etc. are not measured)

@@

> However, the magnitudes of these differences are similar and relatively modest across alternate samples. Restricting our sample to retired households balances concerns about sample selection and measurement error. 
[(p.19)](BarthPapageorgeThom_SNPWealth_JPE2020.pdf#page=19)
